\documentclass[12pt,oneside,a4paper]{article}
%
\input{page_layout}

\docname{Cost specification}


\begin{document}

\thispagestyle{empty}


\section*{Cost specification}

\subsection*{Salaries}
%
The project is set-up around Inderpreet Kaur and a dominating part of the
project costs consist of her salary. Her present position ends 2022-03-15. If
this application is approved, her position will be extended with two years.
That is, this project will run over two years, between 2022-03-16 to
2024-03-15. A 80\% funding is sought for her, to leave some room for being
involved in teaching and other projects.

I.\ Kaur will be in charge of the practical work. She will be supported by
Luisa Ickes, Leif Eriksson and Patrick Eriksson, that will contribute to e.g.\
planning, feedback, data analysis and article writing, but also some practical
input is foreseen. To cover this work, the application includes a 5\% funding
for them. With one exception, the funding is set to 10\% for Leif Eriksson
during 2022, as he will be in charge of setting up and testing the
classificating of SAR images. The actual time Luisa Ickes, Leif Eriksson and
Patrick Eriksson will spend on the project is expected to be larger than what
the application covers. The additional time will be covered by faculty funding.




\subsection*{Other costs}
%
Costs for rooms and IT infrastructure are at Chalmers based on salaries
(6\%).

One conference or workshop trip per year is assumed, with a cost of 15\,kkr for
each trip. The cost of three journal articles (18\,kkr each) are included. The
university applies no overhead on the costs.

\end{document}

